---
title: "connect2postgres2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{connect2postgres2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `connect2postgres2` is a helpful command that trys to connect to the database specified. It relies on the functions `getPassword`, `get_pgpass` to see if you already defined the connection and password information needed (in the secure `pgpass` file that can hold this confidential info) and if it find the info it passes it on to the `connect2postgres` function.

First it is good to test things out: 

```{r setup, eval = F}
library(cardatdbtools)
if(!require("RPostgreSQL")) install.packages("RPostgreSQL"); library("RPostgreSQL")

username <- "postgis_user"

pwd <- get_pgpass(database = "postgis_car",
                  host = "swish4.tern.org.au",
                  user = username,
                  remote = TRUE,
                  savePassword = TRUE)

ch <- connect2postgres(
                 hostip = pwd[,1],
                 db = pwd[,3],
                 user = pwd[,4],
                 p = pwd[,5])

rm(pwd) # remove the password

dbGetQuery(ch, "select * from public.dbsize ")
```


Now the function can be used as a shortcut:

```{r, eval = F}
library(cardatdbtools)
ch <- connect2postgres2("postgis_car")
```